Correlations between PTBP at different resolutions

### 2020-07-31 Scripts_for_results/01_creating_table_of_data_summaries.Rmd
updated results

domains <- readRDS("/home/stilianoudakisc/TAD_data_analysis/peakachu/peakachu_GM12878.rds")

@@

domains <- readRDS("/home/stilianoudakisc/TAD_data_analysis/peakachu/peakachu_K562.rds")

@@

## LOLLIPOP

domains <- readRDS("/home/stilianoudakisc/TAD_data_analysis/lollipop/lollipop_GM12878.rds")

domains <- readRDS("/home/stilianoudakisc/TAD_data_analysis/lollipop/lollipop_K562.rds")

>>>>

domains <- readRDS("Z:/TAD_data_analysis/peakachu/peakachu_GM12878.rds")

@@

domains <- readRDS("Z:/TAD_data_analysis/peakachu/peakachu_K562.rds")

@@

### 2020-07-31 Scripts_for_results/04_creating_rfe_lineplot.Rmd
updated results

## LOLLIPOP

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("GM12878")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_lollipop.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

```{r}
chrs <- paste0("CHR",c(1:8,10:22))
rfeperchr <- data.frame()
for(i in c("K562")){
  for(k in 1:length(chrs)){print(c(i,k));
    rfeModelResultsList <- readRDS(paste0("Z:/TAD_data_analysis/",
                                          i,
                                          "/",
                                          "10kb/results_by_chr/",
                                          chrs[k],
                                          "/rus/distance/TADrfe_lollipop.rds"))
    rfeModelResults <- rfeModelResultsList[[1]]
    rfeModelResults <- rfeModelResults[,c(1,11)]
    rfeModelResults$CL <- i
    rfeModelResults$Chromosome <- chrs[k]
    rfeperchr <- rbind.data.frame(rfeperchr, rfeModelResults)
  }
}

@@

>>>>

@@

# Plotting

```{r}
rfeperchr_summ_arrowhead <- rfeperchr_summ
rfeperchr_summ_peakachu <- rfeperchr_summ

rfeperchr_summ_gm12878 <- rbind.data.frame(rfeperchr_summ_arrowhead,rfeperchr_summ_peakachu)
rfeperchr_summ_gm12878$Tool <- c(rep("ARROWHEAD", nrow(rfeperchr_summ_arrowhead)),
                                 rep("PEAKACHU", nrow(rfeperchr_summ_peakachu)))

ggplot(rfeperchr_summ_gm12878, aes(x=Variables, y=Performance, color=Tool)) + 
  geom_line(size=2,) +
  geom_point(size=4, position = position_dodge(.9)) +
  geom_errorbar(aes(ymin=Performance-(PerformanceSD+.01), ymax=Performance+(PerformanceSD+.01)), 
                width=4, 
                size=1,
                position = position_dodge(.9)) +
  xlab("Number of top ranked annotations") +
  ylab("Cross-Validated BA") +
  scale_color_manual(name="Boundary Type", 
                       values=c("blue", "red"))+
  scale_x_continuous(breaks = c(2,4,8,16,32,52),
                     labels = c(2,4,8,16,32,52))+
  theme_minimal() +
  theme_bw()+
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.x = element_text(size = 20),
        axis.title.y = element_text(size = 20),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        #strip.text.x = element_text(size = 15),
        #panel.spacing = unit(2, "lines"),
        legend.text=element_text(size=15),
        legend.title=element_text(size=20),
        plot.title = element_text(size=20),
        legend.position = "right")
```

### 2020-07-31 Scripts_for_results/06_creating_enriched_heatmaps.Rmd
updated results

  norm_mat <- normalizeToMatrix(annotations, 
                                boundaries, 
                                value_column = "coverage", 
                                extend = e*1000, 
                                w = 50,
                                mean_mode = "w0",
                                keep = c(0,.999))
  EH <- EnrichedHeatmap(norm_mat, 
                        col = ifelse(ct=="ARROWHEAD" | ct=="PEAKACHU" | ct=="LOLLIPOP", c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)),
                                     c("black",colorRampPalette(c("white", "pink", "red"))(99))), 
                        #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                        row_title="Boundaries",
                        show_heatmap_legend = FALSE,
                        row_title_side="left", 
                        column_title=ct, 
                        axis_name = axis_names,
                        column_title_gp = gpar(fontsize = 10),
                        row_title_gp = gpar(fontsize = 10),
                        axis_name_gp = gpar(fontsize = 10),
                        top_annotation = HeatmapAnnotation(lines = anno_enriched(gp = gpar(col = ifelse(ct=="ARROWHEAD", "blue", "red"), 
                                                                                           fontsize = 10,
                                                                                           lwd = 2), 
                                                                                 axis_param = list(side = "right",
                                                                                                   facing = "inside"))))
  return(EH)
}

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

>>>>

  norm_mat <- normalizeToMatrix(annotations, 
                                boundaries, 
                                value_column = "coverage", 
                                extend = e*1000, 
                                w = 50,
                                mean_mode = "w0",
                                keep = c(0,.999))
  EH <- EnrichedHeatmap(norm_mat, 
                        col = ifelse(ct=="ARROWHEAD" | ct=="PEAKACHU" | ct=="LOLLIPOP", c("black",colorRampPalette(c("white", "lightblue", "blue"))(99)),
                                     c("black",colorRampPalette(c("white", "pink", "red"))(99))), 
                        #heatmap_legend_param = list(show_heatmap_legend = FALSE),
                        row_title="Boundaries",
                        show_heatmap_legend = FALSE,
                        row_title_side="left", 
                        column_title=ct, 
                        axis_name = axis_names,
                        column_title_gp = gpar(fontsize = 10),
                        row_title_gp = gpar(fontsize = 10),
                        axis_name_gp = gpar(fontsize = 10),height=unit(2, "in"),
                        width=unit(2, "in")
                        top_annotation = HeatmapAnnotation(height=unit(2, "in"),
                                                           width=unit(2, "in"),
                                                           lines = anno_enriched(gp = gpar(col = ifelse(ct=="ARROWHEAD", "blue", "red"), 
                                                                                           fontsize = 10,
                                                                                           lwd = 2), 
                                                                                 axis_param = list(side = "right",
                                                                                                   facing = "inside"))))
  return(EH)
}

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout.rds"))

### 2020-07-31 Scripts_for_results/07_creating_distance_to_chipseq.Rmd
updated results

pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("preciseTAD", "ARROWHEAD"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(2:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))

@@

pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("preciseTAD", "PEAKACHU"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

>>>>

pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("ARROWHEAD", "preciseTAD"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout.rds"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))

@@

pred_v_called_df$BoundReg <- factor(pred_v_called_df$BoundReg, levels=c("PEAKACHU", "preciseTAD"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(2:8,10,11,13:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))

### 2020-07-31 Scripts_for_results/08_creating_venn_diagrams.Rmd
updated results

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD.rds"))

@@

@@

@@

@@

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(21:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_peakachu.rds"))

@@

## LOLLIPOP

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_lollipop.rds"))

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
chrs <- paste0("CHR", c(2:8,10:15,17:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_lollipop.rds"))

### Within cell line (preciseTAD vs LOLLIPOP)

@@

res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878,
                                  all_true_bounds_gm12878),
                       NameOfPeaks=c("preciseTAD", "LOLLIPOP"))

@@

res <- makeVennDiagram(Peaks=list(all_pred_bounds_k562,
                                  all_true_bounds_k562),
                       NameOfPeaks=c("preciseTAD", "LOLLIPOP"))

@@

###### LOLLIPOP

>>>>

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout.rds"))

@@

### Across cell line

@@

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "lightblue"
gp[["Face"]][["10"]]$fill <-  "red"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- .1
gp[["SetText"]][["Set2"]]$cex <- .1

@@

genomicCorr.jaccard(all_pred_bounds_gm12878,all_pred_bounds_k562)

@@

genomicCorr.jaccard(all_true_bounds_gm12878,all_true_bounds_k562)
```

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))

@@

```{r}
pred_bound_list <- GRangesList()
true_bound_list <- GRangesList()
chrs <- paste0("CHR", c(1:8,10:22))
for(i in 1:length(chrs)){
  called_and_pred <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout_peakachu.rds"))

@@

### Nesting between pt(arrowhead) and pt(peakachu)

@@

res <- makeVennDiagram(Peaks=list(all_pred_bounds_gm12878_a,
                                  all_pred_bounds_gm12878_p),
                       NameOfPeaks=c("preciseTAD", "PEAKACHU"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "red"
gp[["Face"]][["10"]]$fill <-  "lightblue"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- .1
gp[["SetText"]][["Set2"]]$cex <- .1

@@

res <- makeVennDiagram(Peaks=list(all_pred_bounds_k562_a,
                                  all_pred_bounds_k562_p),
                       NameOfPeaks=c("preciseTAD", "PEAKACHU"))

venn.pt <- venn_cnt2venn(res$vennCounts)
venn.pt <- compute.Venn(venn.pt)
gp <- VennThemes(venn.pt)
gp[["Face"]][["11"]]$fill <-  "purple"
gp[["Face"]][["01"]]$fill <-  "red"
gp[["Face"]][["10"]]$fill <-  "lightblue"
gp[["FaceText"]][["10"]]$cex <- 2
gp[["FaceText"]][["11"]]$cex <- 2
gp[["FaceText"]][["01"]]$cex <- 2
gp[["SetText"]][["Set1"]]$cex <- .1
gp[["SetText"]][["Set2"]]$cex <- .1

@@

# Jaccard Indices

```{r}
genomicCorr.jaccard = function(query, reference, restrict = NULL) {
  if(is.null(restrict)) {
    res = sum(width(GenomicRanges::intersect(query, reference))) / sum(as.numeric(width(GenomicRanges::union(query, reference))))
  } else {
    gr1 = GenomicRanges::intersect(query, reference)
    gr1 = GenomicRanges::intersect(gr1, restrict)

    gr2 = GenomicRanges::union(query, reference)
    gr2 = GenomicRanges::intersect(gr2, restrict)
    res = sum(width(gr1)) / sum(width(gr2))
  }
  return(res)
}

chrs <- paste0("CHR", c(1:8,10:22))
ji_pred <- numeric()
ji_true <- numeric()
for(i in 1:length(chrs)){
  called_and_pred_gm12878 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/",
                                    chrs[i],
                                    "/rus/distance/preciseTAD_holdout.rds"))

  called_and_pred_k562 <- readRDS(paste0("Z:/TAD_data_analysis/K562/5kb/results_by_chr/",
                                            chrs[i],
                                            "/rus/distance/preciseTAD_holdout.rds"))

  called_and_pred_gm12878[[2]] <- flank(called_and_pred_gm12878[[2]], 5000, both=TRUE)
  called_and_pred_gm12878[[3]] <- flank(called_and_pred_gm12878[[3]], 5000, both=TRUE)
  called_and_pred_k562[[2]] <- flank(called_and_pred_k562[[2]], 5000, both=TRUE)
  called_and_pred_k562[[3]] <- flank(called_and_pred_k562[[3]], 5000, both=TRUE)

  ji_pred[i] <- genomicCorr.jaccard(called_and_pred_gm12878[[2]],called_and_pred_k562[[2]])
  ji_true[i] <- genomicCorr.jaccard(called_and_pred_gm12878[[3]],called_and_pred_k562[[3]])
}

summary(ji_pred)
summary(ji_true)
wilcox.test(ji_pred,ji_true)

##############################################################################################

chrs <- paste0("CHR", c(1:8,10:22))
ji_pred <- numeric()
ji_true <- numeric()
for(i in 1:length(chrs)){
  called_and_pred_gm12878 <- readRDS(paste0("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/",
                                            chrs[i],
                                            "/rus/distance/preciseTAD_holdout_peakachu.rds"))

  called_and_pred_k562 <- readRDS(paste0("Z:/TAD_data_analysis/K562/10kb/results_by_chr/",
                                         chrs[i],
                                         "/rus/distance/preciseTAD_holdout_peakachu.rds"))

  called_and_pred_gm12878[[2]] <- flank(called_and_pred_gm12878[[2]], 10000, both=TRUE)
  called_and_pred_gm12878[[3]] <- flank(called_and_pred_gm12878[[3]], 10000, both=TRUE)
  called_and_pred_k562[[2]] <- flank(called_and_pred_k562[[2]], 10000, both=TRUE)
  called_and_pred_k562[[3]] <- flank(called_and_pred_k562[[3]], 10000, both=TRUE)

  ji_pred[i] <- genomicCorr.jaccard(called_and_pred_gm12878[[2]],called_and_pred_k562[[2]])
  ji_true[i] <- genomicCorr.jaccard(called_and_pred_gm12878[[3]],called_and_pred_k562[[3]])
}

summary(ji_pred)
summary(ji_true)
wilcox.test(ji_pred,ji_true)

### 2020-07-31 Scripts_for_results/11_correlations_across_resolutions.Rmd
updated results

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)
library(ComplexHeatmap)
library(circlize)
library(cotools)
library(ggcorrplot)

@@

```{r}
gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")
gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/CHR22/rus/distance/preciseTAD_holdout.rds")

>>>>

```{r}
library(S4Vectors)
library(GenomicRanges)
library(ggplot2)
library(caret)
library(randomForest)
library(glmnet)
library(gbm)
library(DMwR)
library(rtracklayer)
library(Biostrings)
library(BSgenome)
library(cluster)
library(pROC)
library(SuperLearner)
library(data.table)
library(PRROC)
library(bigmemory)
library(ranger)
library(dplyr)
library(parallel)
library(doSNOW)
library(foreach)
library(pbapply)
library(ggpubr)
library(scales)
library(GGally)
library(VennDiagram)
library(network)
library(sna)
library(gtable)
library(grid)
library(magrittr) 
library(DT)
library(tidyverse)
library(reshape)
library(ROSE)
library(lattice)
library(corrplot)
library(cluster)
library(RColorBrewer)
library(GenometriCorr)
library(ggsignif)
library(Vennerable)
library(VennDiagram)
library(ChIPpeakAnno)
library(EnrichedHeatmap)
library(ComplexHeatmap)
library(circlize)
library(cotools)
library(ggcorrplot)
library(circlize)

@@

```{r}
gm12878_5kb <- readRDS("Z:/TAD_data_analysis/GM12878/5kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
gm12878_10kb <- readRDS("Z:/TAD_data_analysis/GM12878/10kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
gm12878_25kb <- readRDS("Z:/TAD_data_analysis/GM12878/25kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
gm12878_50kb <- readRDS("Z:/TAD_data_analysis/GM12878/50kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
gm12878_100kb <- readRDS("Z:/TAD_data_analysis/GM12878/100kb/results_by_chr/CHR1/rus/distance/preciseTAD_holdout.rds")
